\input{HeadMatter.tex}
	
\begin{flushleft}
\Large\textbf{Assignment 6 - Door of the future with Pronto Doors (25\%)}\\
\end{flushleft}

This project is being run in conjunction with the Studio 3 project of the same name.\\

The key deliverables of this project are therefore:

\begin{enumerate}
	\item Three (3) photo-realistic images of your door design 
	\item 30 second animation to showcase your design from all sides. A simple product rotation will suffice
	\item A 3D print of either the entire door or key design features.  I will advise depending on the nature of your design.
\end{enumerate}

Please note that this project will take a considerable amount of time to complete.\\

\textbf{Suggested Production Workflow}\\
I suggest you adopt a structured approach similar to that shown below:

\begin{itemize}
	\item Follow the methodology outlined in the Masterpiece assignment.
	\item As part of that process, create 3D prints of key features of your design in order to allow yourself an opportunity to resolve the design further.  Your final 3D print should be informed by these prints and models
	\item The animation should be completed at the end of the design process; i.e. once you have a fully resolved design.  You should use Microsoft Movie Maker or Adobe Premier Pro to create professional grade animations that include title sequence and credit sequence.
\end{itemize}

\input{FileSetup.tex}

\input{LateSubmission.tex}

\textbf{Factors that will be considered when marking}\\
\begin{itemize}
	\item Realism of images
	\item Lighting, Materials, Composition, etc.
	\item Professionalism of animation
	\item Quality of 3D prints and ability to showcase the design and/or key features.
\end{itemize}


\end{document}