\input{HeadMatter.tex}
	
\begin{flushleft}
\Large\textbf{Assignment 4 - CareBright Unity Game Engine (10\%)}\\
\end{flushleft}

This assignment is in conjunction with the CareBright project set in Design Studio 3.  The marks allocated to this subject are separate to the mark allocation in Design Studio 3.\\

In this assignment you are required to create a PC Game version of your design solution as developed for the CareBright project.\\

In order to complete this assignment, I suggest the following work-flow:

\begin{itemize}
	\item Perfect your model in 3D Studio
	\item Convert all materials in 3D Studio to 'Standard' using the AMC converter script available in 3DS
	\item Export your model as an FBX, excluding all cameras, lights, animations etc.
	\item Import your model into Unity, setup the FPS controller
	\item Relight your game within unity
	\item Add a menu system, and scenes as necessary
\end{itemize}

Submission is to be a single zip file containing the game and all game assets.  Please note that this will be a very large pack and alternative methods of submission may be necessary.  Should this be the case, keep an eye on your email and Moodle forum for information.\\

The submission date for this project is posted on Moodle.\\

\textbf{EXTRA CREDIT}\\
Subject to completion of the above, an additional 5\% will be awarded for the successful completion of \textbf{one} of the following:
\begin{enumerate}
	\item Creation of a Android VR version of your game submission.  The VR version must be created using Google VR.  Character movement, and menus are not necessary.
	\item Creation of an appropriate AR Android application to showcase your design.  Your AR must use Android and the Vuforia toolkit.
\end{enumerate}

\end{document}